\begin{titlepage}
  \begin{center}
  \vspace*{3cm}
  % Gamma-ray Spectral Analysis of Three Energetic Millisecond Pulsars
  \Large \textbf{IDENTIFY EXOPLANET CANDIDATES \\[0.5cm]WITH DEEP LEARNING MODELS\\[0.5cm]}
  \small
    A THESIS \\[0.5cm] 
    SUBMITTED TO THE DEPARTMENT OF PHYSICS \\[0.5cm]
    OF THE UNIVERSITY OF HONG KONG \\[0.5CM]
    IN PARTIAL FULFILLMENT OF THE REQUIREMENTS \\[0.5cm]
    FOR THE DEGREE OF \\[0.5cm]
    DOCTOR OF PHILOSOPHY \\[4.2cm]

    By \\[0.5cm]
    \large Wenchao Wang \\[0.5cm]
    August 2021
    \newpage 
    \centering 
    Abstract of thesis entitled \\[1.2cm]
    \Large \textbf{IDENTIFY EXOPLANET CANDIDATES \\[0.5cm]WITH DEEP LEARNING MODELS\\[0.5cm]}
    \normalsize Submitted by \\ [0.5cm]
    \Large \textbf{Wenchao Wang} \\[1cm]
    \normalsize for the degree of Doctor of Philosophy \\[0.5cm]
    at the University of Hong Kong \\[0.5cm]
    in August 2021 \\[1.9cm]
  \end{center}

    % abstract
    \doublespacing
    \noindent The work is about identifying planet candidates using deep learning models.
Finding these objects manually is a very labor intensive task.
For example, \textit{The Large
    Synoptic Survey Telescope (LSST)} is expected to generate about
$200,000$ images per year, which is equivalent of more than
$10^{6}$ GB of data. Therefore using reliable algorithms to
manage the data is necessary. Deep learning can be helpful
because it suits well for very large input data. In general,
having more data only makes deep learning models perform better.

\vspace{\baselineskip}

\noindent We use \textit{Kepler Space Telescope} and
\textit{Transiting Exoplanet Survey Satellite} (\textit{TESS})
to detect planet candidates by using a convolutional neural
network model. We apply the Q1-Q17 (DR24) table as our training
and test sets. The model takes
two phase-folded light curves and some parameters of each transit-like signal
and then outputs whether the signal represents a planet candidate (PC), 
a non-transiting phenomena (NTP) or a false positive (FP).
In the current model, we feed 17 features into a dense neural network
model, such as transit durations and depth of signals.
At this stage, the models achieve AUROC and accuracy
of about $97.7\%$, $95.9\%$ respectively for the test set.
The accuracy for the training set can be over $99\%$, which means that
the model can easily overfit the data. The most straightforward way to the
problem is to use more data to train the model.
Therefore, we plan to train it with more simulated data later in order to
increase the AUROC and accuracy of predictions.
    
\end{titlepage}